Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model.

### 2014-04-22 paper_enahpc14/Sec3:Measurement-framework.tex
cancels previous commits of Cristiano as IBM Zurich is actually not going to contribute to this work

\subsubsection{University of Hamburg}
To assess the  performance and the energy efficiency  of COSMO-ART, we
employ   a    version   of   the    integrated   framework   presented
in~\cite{energy13}  that  works in  combination  with Extrae  and
Paraver,   which  are   profiling/tracing   and  visualization   tools,
respectively.
%The left part of the \vref{fig:Lustre} offers a graphical representation of
%the Lustre architecture; the right depicts the tracing and profiling framework.
To  use our  approach,  COSMO-ART is  compiled  using the  Extrae
compiler wrappers, which automatically  instrument the Fortran code of
the  model. Next,  COSMO-ART is  run  on the  nodes, thus  dissipating
certain  amount of  power.  These  nodes are connected  to power 
measurement  devices that  account for  the dissipated power/consumed 
energy and  send the power data  to the tracing  server. The client, 
meanwhile, sends start/stop primitives in order to gather captured data
by the wattmeters onto the tracing server, where an  instance of the 
\pmlib server  is running.

>>>>

\subsubsection{University of Hamburg}
To assess the  performance and the energy efficiency  of COSMO-ART, we
employ   a    version   of   the    integrated   framework   presented
in~\cite{energy13} that works in  combination with Extrae and Paraver,
which are profiling/tracing and visualization tools, respectively.

%The left part of the \vref{fig:Lustre} offers a graphical representation of
%the Lustre architecture; the right depicts the tracing and profiling framework.
To use our  approach, COSMO-ART is compiled using  the Extrae compiler
wrappers,  which  automatically instrument  the  Fortran  code of  the
model. Next, COSMO-ART  is run on the nodes,  thus dissipating certain
amount  of power.   These  nodes are  connected  to power  measurement
devices that account for the dissipated power/consumed energy and send
the power  data to  the tracing server.  The client,  meanwhile, sends
start/stop  primitives  in  order  to  gather  captured  data  by  the
wattmeters onto  the tracing server,  where an instance of  the \pmlib
server is running.

### 2014-04-22 paper_enahpc14/paper.tex
cancels previous commits of Cristiano as IBM Zurich is actually not going to contribute to this work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{xspace}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the Performance  and Energy Efficiency of COSMO-ART,
  a Coupled Numerical Weather Forecast and Chemical Transport Model}
% \thanks{This work was supported by the EU Project FP7 318793 ``EXA2GREEN''}}
%\subtitle{Write here subtitle}

@@

\author{Joseph~Charles \and William~Sawyer \and Manuel~F.~Dolz \and
  Sandra~Catal\'an \and Cristiano~Malossi }

@@

\institute{J.~Charles, W.~Sawyer 
	\at Swiss National Supercomputing Centre (CSCS)
	\\ CH-6900 Lugano, Switzerland  
 	\\ E-mails:~{\{joseph.charles,william.sawyer\}@cscs.ch} 
        \and M.~F.~Dolz 
        \at Dept. of Informatics, University of Hamburg (UHAM)
	\\ DE-22527 Hamburg, Germany
        \\ \email{manuel.dolz@informatik.uni-hamburg.de}  
        \and S.~Catal\'an
        \at Jaume I University of Castell\'on (UJI)
	\\ ES-12071 Castell\'on, Spain
        \\ \email{catalans@icc.uji.es}
        \and C.~Malossi  
        \at IBM Zurich Research Laboratory 
        \\ CH-8000 Zurich, Switzerland
        \\ \email{ACM@zurich.ibm.com}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}
%
\smartqed
%
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}
\usepackage{xspace}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but \newcommand{}{}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the Performance and Energy Efficiency of COSMO-ART,
  a Coupled Numerical Weather Forecast and Chemical Transport Model.}
%\thanks{}
%\subtitle{}

@@

\author{Joseph~Charles \and William~Sawyer \and Manuel~F.~Dolz \and
  Sandra~Catal\'an}

@@

\institute{J.~Charles, W.~Sawyer
	\at Swiss National Supercomputing Centre (CSCS)
	\\ CH-6900 Lugano, Switzerland
 	\\ E-mails:~{\{joseph.charles,william.sawyer\}@cscs.ch}
        \and M.~F.~Dolz
        \at Dept. of Informatics, University of Hamburg (UHAM)
	\\ DE-22527 Hamburg, Germany
        \\ \email{manuel.dolz@informatik.uni-hamburg.de}
        \and S.~Catal\'an
        \at Jaume I University of Castell\'on (UJI)
	\\ ES-12071 Castell\'on, Spain
        \\ \email{catalans@icc.uji.es}
}
